D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-08 ootavacuous.tex
"Why rfe" appendix: It is not the compiler, but the implementation
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Although the examples presented in
Section~\ref{sec:OOTA: rf vs. rfe}
(and shown as litmus tests in
Listings~\ref{lst:OOTA With an Intra-Process Store-Load Link}
and~\ref{lst:OOTA With an Intra-Process Store-Load Link, Optimized})
demonstrate that rf can be atemporal, they demonstrate neither
OOTA cycles nor OOTA-like behavior in full C++ compilers.
This appendix provides more involved examples that can be optimized
so as to demonstrate OOTA-like behavior.

@@

In the confines of the C++ abstract machine (omitting the no-OOTA
restriction), this allows a value-17 OOTA cycle, courtesy of the fact
that C++ respects neither control nor data dependencies.
However, the \co{herd7} tool does not identify this cycle, perhaps due
to its restrictions on its handling of arithmetic on OOTA values.

>>>>

Although the examples presented in
Section~\ref{sec:OOTA: rf vs. rfe}
(and shown as litmus tests in
Listings~\ref{lst:OOTA With an Intra-Process Store-Load Link}
and~\ref{lst:OOTA With an Intra-Process Store-Load Link, Optimized})
demonstrate that rf can be atemporal, they demonstrate neither
OOTA cycles nor OOTA-like behavior in compiler-based C++ implementations.
This appendix provides more involved examples that can be optimized
so as to demonstrate OOTA-like behavior.

@@

Within the confines of the C++ abstract machine (omitting the no-OOTA
restriction), this allows a value-17 OOTA cycle, courtesy of the fact
that C++ respects neither control nor data dependencies.
However, the \co{herd7} tool does not identify this cycle, perhaps due
to its restrictions on its handling of arithmetic on OOTA values.
